Appendix 4: Model Comparison Code For Manuscript

### 2025-09-03 manuscript_code.Rmd
Incorporating additional Australian data

---
title: 'Appendix 2: Manuscript and Exploratory Code'
author: "Abigail Edwards, Lauri Hietajärvi and Mikko Arvas"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time())`"
output:
  pdf_document:
    toc: true
  html_document:
    toc: true
    df_print: paged
always_allow_html: true
---

@@

data.fit3 <- data.fit2 %>%
  select(-ss_psycown,
         -ss_selfid, 
         -ss_intention,
         -ss_donation)

corrplot(cor(data.fit3,use="pairwise.complete.obs"))
mcar_test(data.fit3 %>% select(-dttma))

@@

>>>>

---
title: 'Appendix 2: Manuscript and Exploratory Code'
author: "Abigail Edwards, Lauri Hietajärvi and Mikko Arvas"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time())`"
output:
  html_document:
    toc: true
    df_print: paged
  pdf_document:
    toc: true
always_allow_html: true
---

@@

data.fit3 <- data.fit2 %>%
  select(-ie01,
         -dttma,
        -ss_psycown,
         -ss_selfid, 
         -ss_intention,
         -ss_donation)

sum(is.na(data.fit3))
sum(!is.na(data.fit3))

corrplot(cor(data.fit3,use="pairwise.complete.obs"))
mcar_test(data.fit3)

@@

knitr::knit_exit()

### 2025-09-03 modelcomparison_code.Rmd
Incorporating additional Australian data

#adding data from previous Australia study 
##note estimates created using lavaan differ very slightly from estimates using process macro (original paper)
manual_data <- tibble(
  est = c(0.343, 0.382, -0.137, 0.657, 0.322, -0.024, 0.073, -0.047, 0.25),
  ci.lower = c(0.227, 0.308, -0.215, 0.531, 0.226, -0.102, 0.035, -0.08, 0.186),
  ci.upper = c(0.459, 0.455, -0.06, 0.782, 0.418, 0.054, 0.11, -0.014, 0.315),
  label = c("manuala1", "manuala2", "manualb1", "manualb2", "manuald21", "manualcp", "manualeff", "manualeff1", "manualeff2"),
  lhs = c("psycown", "selfid", "intention", "intention", "selfid", "intention", "ind_eff", "ind_eff1", "ind_eff2"),
  rhs = c("donation", "donation", "psycown", "selfid", "psycown", "donation", "a1*d21*b2", "a1*b1", "a2*b2"),
  op = c("~", "~", "~", "~", "~", "~", ":=", ":=", ":="),
  term = c("a1:psycown~donation", "a2:selfid~donation", "b1:intention~psycown", "b2:intention~selfid", "d21:selfid~psycown", "cp:intention~donation", "ind_eff:=a1*d21*b2", "ind_eff1:ind_eff1:=a1*b1", "ind_eff2:ind_eff2:=a2*b2"),
  #estmet = factor("Manual", levels = levels(data.forest$estmet)),
  estmet = "Bootstrapped",
  missing = "Listwise",
  linetype = "Sum score",
  sample = "Australia",
  #mtype = factor("Manual-Manual-Manual", levels = levels(data.forest$mtype)),
  #color = factor("Manual and Manual", levels = levels(data.forest$color)),
  hollow_group = NA
)

@@

data.forest <- bind_rows(data.forest, manual_data)

>>>>

#adding data from previous Australia study

#Previously Reported Effects (Sum score, bootstrapped, listwise)
##note estimates created using lavaan differ very slightly from estimates using process macro (original paper)
manual_data1 <- tibble(
  est = c(0.343, 0.382, -0.137, 0.657, 0.322, -0.024, 0.073, -0.047, 0.25),
  ci.lower = c(0.227, 0.308, -0.215, 0.531, 0.226, -0.102, 0.035, -0.08, 0.186),
  ci.upper = c(0.459, 0.455, -0.06, 0.782, 0.418, 0.054, 0.11, -0.014, 0.315),
  label = c("manual1a1", "manual1a2", "manual1b1", "manual1b2", "manual1d21", "manual1cp", "manual1eff", "manual1eff1", "manual1eff2"),
  lhs = c("psycown", "selfid", "intention", "intention", "selfid", "intention", "ind_eff", "ind_eff1", "ind_eff2"),
  rhs = c("donation", "donation", "psycown", "selfid", "psycown", "donation", "a1*d21*b2", "a1*b1", "a2*b2"),
  op = c("~", "~", "~", "~", "~", "~", ":=", ":=", ":="),
  term = c("a1:psycown~donation", "a2:selfid~donation", "b1:intention~psycown", "b2:intention~selfid", "d21:selfid~psycown", "cp:intention~donation", "ind_eff:=a1*d21*b2", "ind_eff1:ind_eff1:=a1*b1", "ind_eff2:ind_eff2:=a2*b2"),
  #estmet = factor("Manual", levels = levels(data.forest$estmet)),
  estmet = "Bootstrapped",
  missing = "Listwise",
  linetype = "Sum score",
  sample = "Australia",
  #mtype = factor("Manual-Manual-Manual", levels = levels(data.forest$mtype)),
  #color = factor("Manual and Manual", levels = levels(data.forest$color)),
  hollow_group = NA
)

#best practice model (latent, robust, fiml)
manual_data2 <- tibble(
  est = c(0.369, 0.373, -0.19, 0.825, 0.341, -0.089, 0.104, -0.07, 0.308),
  ci.lower = c(0.25, 0.279, -0.298, 0.696, 0.22, -0.183, 0.048, -0.117, 0.23),
  ci.upper = c(0.487, 0.467, -0.081, 0.954, 0.461, 0.004, 0.159, -0.023, 0.386),
  label = c("manual2a1", "manual2a2", "manual2b1", "manual2b2", "manual2d21", "manual2cp", "manual2eff", "manual2eff1", "manual2eff2"),
  lhs = c("psycown", "selfid", "intention", "intention", "selfid", "intention", "ind_eff", "ind_eff1", "ind_eff2"),
  rhs = c("donation", "donation", "psycown", "selfid", "psycown", "donation", "a1*d21*b2", "a1*b1", "a2*b2"),
  op = c("~", "~", "~", "~", "~", "~", ":=", ":=", ":="),
  term = c("a1:psycown~donation", "a2:selfid~donation", "b1:intention~psycown", "b2:intention~selfid", "d21:selfid~psycown", "cp:intention~donation", "ind_eff:=a1*d21*b2", "ind_eff1:ind_eff1:=a1*b1", "ind_eff2:ind_eff2:=a2*b2"),
  #estmet = factor("Manual", levels = levels(data.forest$estmet)),
  estmet = "Robust",
  missing = "FIML",
  linetype = "Latent factor",
  sample = "Australia",
  #mtype = factor("Manual-Manual-Manual", levels = levels(data.forest$mtype)),
  #color = factor("Manual and Manual", levels = levels(data.forest$color)),
  hollow_group = NA
)

@@

data.forest <- bind_rows(data.forest, manual_data1, manual_data2)
